
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Present}   {Senior AI Engineer | Senior}{Agile Insights}{Remote}
    {September 2024} {
                      \begin{itemize}
					    \item Lead the development of our cutting edge AI solution Agile AI-One used by government agencies. Contributed to existing open source projects \& internal IP.
						\item Using Azure AI Services \& Document Intelligence to process documents with OCR extracting capabilites and Speech Intelligence for voice to text translation. Utilising Semantic Kernel with yaml Handlebars prompting to develop agents and agentic applications.
						\item Implementing safety features with Azure Open AI which includes Content Filtering and Prompt Injection Shielding to ensure safe and secure use of Gen AI.
						\item Maintained the backend solution architecture for our internal AI project utilising DDD and Clean Architecture principles with .NET Minimal APIs and AI chat event streaming.
                        \item Coordinated the integration of Semantic search/Hybrid search \& RAG techniques in Azure AI Search. Developed a powerful custom indexing solution for data ingestion from blob storage. Applied a Message-Queue for heavy write scenarios to be able to ingest thousands of files with minimal load and redundancy support.
                      \end{itemize}
                    }
                    {.NET 8,MediatR,CQRS,Semantic Kernel,Azure AI Search,Document Intelligence,Speech Intelligence,Azure AI Services,CosmosDB,React,DDD,Generative AI,Message Queues,Azure Service Bus}
  \emptySeparator
\experience
    {Present}   {Founder | CEO}{GitYas}{Remote}
    {August 2023} {
                      \begin{itemize}
					    \item Founder of a cross-platform Git GUI desktop application built with a Rust backend \& a React Vite frontend using ShadCN \& Tailwind CSS components.
						\item Implemented OAuth2 with GitHub integration for connecting to repositories, viewing commits, pushing, merging, branching, tagging and stashing.
						\item Using advanced data structures and algorithms to implement a directed acyclic graph to visualise commits on a HTML canvas.
						\item Achieved efficiency using crates such as notify-rs to implement operating system level file listeners to listen to file changes and provide real time UI feedback.
                        \item Working with asynchronous functions using tokio, idiomatic error handling using anyhow, lifetime and borrowing management rules on Rust \& secure key storage on operating systems credentials storage using the keyring crate.
                      \end{itemize}
                    }
                    {Rust,Tauri,crates,React,Vite,tokio,git2-rs,notify-rs,serde,keyring,reqwest,anyhow}
  \emptySeparator
  \experience
    {September 2024}   {.NET Developer \& AI | Mid-Senior}{preezie}{CBD Melbourne}
    {August 2022} {
                      \begin{itemize}
					    \item Championed the AI project at preezie, leveraging semantic kernel and facilitating monthly Microsoft meetings from Redmond USA to remain at the forefront of technology advancements in Generative AI. Implemented advanced prompt engineering techniques, Vector search with embeddings, Retrieval Augmented Generation (RAG), AI Agents, Semantic search and more.
                        \item Developed innovative solutions using microservices and clean architecture, enhancing existing legacy systems while integrating modern technologies like Angular and React for both backend and frontend development.       
                        \item Solely migrated large scale analytics data to a more cost effective cloud architecture, reducing monthly expenses by 40\% with minimal downtime.
                        \item Single-handedly re-architected and optimized a critical legacy software system, improving and cutting import speeds by over 50\% and ensuring future scalability while collaborating closely with senior leadership. Lead backend developer for a successful new product, nextbuy, contributing to significant ARR growth and achieving cash flow positivity.                                                                   
                      \end{itemize}
                    }
                    {.NET 6/7/8,Elastic Search,Redis,CosmosDB,Semantic Kernel,React \& Angular,PostgreSQL,DDD,Artificial Intelligence}
  \emptySeparator
  \experience
    {August 2022} {Software Engineer}{Motorola Solutions}{Burwood Melbourne}
    {March 2021}    {
                      \begin{itemize}
                        \item Co-developed a multi-tenancy-enabled full-stack solution for CrimeStoppers Tasmania's online crime reporting platform, garnering media recognition and awards. Designed for public anonymity, the platform features real-time report processing, media upload capabilities, and advanced management tools.
                        \item Modernized a legacy product to enhance customer service, transitioning it from a Winforms application into a web application with fine-grained permission controls and Google account authentication. Improved productivity and decreased support needs significantly.
                        \item Managed over-the-air updates for RACV-owned tablets, implementing necessary software patches and security updates through client liaison, ensuring device functionality and security compliance.
                        \item Working closely with mission-critical clients such as Ambulance Victoria, Victoria Police and Fire Rescue Victoria doing UAT Tests for software patches. Following close guidelines and liaising with staff to ensure efficient speedy delivery of patches.
                        \item Developed a web application to efficiently configure hundreds of routers to be installed in Ambulance Victoria vehicles. The app performed various file I/O reading and writing in an easy to use user interface.
                      \end{itemize}
                    }
                    {.NET 5/6,Angular,MongoDB,SQL Server,OAuth2.0,Identity Server,Devops,CI/CD,WPF,Winforms}
  \emptySeparator
  \experience
    {March 2021}     {Software Developer}{Trade View}{St Kilda Melbourne}
    {January 2021}    {
                      \begin{itemize}
                        \item Developing and testing algorithmic trading bots using key indicators and various tactics learned during the job.
                        \item Addressing customer support tickets on a daily basis. Assisting customers with their algorithms and debugging code.
                        \item Adding features to their custom developed CMS system.
                        \item Helped develop and launch a crypto trading site integrating live feeds and price tracking. 
                      \end{itemize}
                    }
                    {Metatrader 5,C,C\#,React,Zoho}
  \emptySeparator
\end{experiences}
