

\cvsection{Projects \& Experience}
\vspace{-0.5\baselineskip}
\begin{cventries}
  \cventry
    {C\#, .NET 7, React \& Angular, Postgres, Hangfire, Microservices, Domain Driven Design, Event Driven Architecture, SQL Server, Cosmos Db, Elastic Search, Redis Cache, Azure Service Bus, Azure Functions, MediatR, CAP, Blob Storage, Open AI, Langchain, Pinecone DB, PostgreSQL, Node.JS, ts.ED}
    {.NET Developer - Preezie}
    {Preezie, Melbourne}
    {Aug. 2022 - Present}
    {
      \begin{cvitems}
        \item {Developing a new improved solution based on asynchronous event-driven microservices, domain driven design and clean architecture practices while maintaining the existing legacy web application.}
        \item {Contributing mainly to backend development with some micro-frontend work in both Angular and React.}
        \item {Main backend developer for a Generative AI POC project investigating the rise of AI generated content and startup competitors. Learned new prompt engineering techniques, Vector search using Open AI Embeddings and various new skills. Solution was one of the many demonstrated by the CEO to investors for potential Series B funding.}
		\item {Migrated hundreds of gigabytes of analytics data to a better cloud service architecture saving up to 40% in costs compared to our previous monthly billings with little downtime.}
        \item {Sole developer of a complex piece of legacy software which parses ecommerce feeds into our system and stores data into elastic search. A critical backbone piece of software that powers our company. Re-architected the solution working closely with the Head Of Technology. Added immense observability and logging to ensure product was solid and future proof. Improved efficiency and speed of importing by more than 2x previous speeds.}
        \item {Lead backend developer of a brand new product (nextbuy) for referring customers on ecommerce checkout pages to other clients. Incorporated various unit tests, observability and logging and modern software-development practices. Product has onboarded 100+ customers so far and has generated an adequate amount of ARR for turning the company cashflow positive.}
	  \end{cvitems}
    }
  \cventry
    {Azure Cosmos DB, SQL database, Blob storage, VNET, Azure Media services, Duende Identity Server 4, .NET 5/6 APIs, Angular, NLog, Azure devops, Automated CI/CD Pipelines, VBA, Winforms, Google OAuth, Angular 13, MJML}
    {Software Engineer}
    {Motorola Solutions, Melbourne}
    {Mar. 2021 - Aug. 2022}
    {
      \begin{cvitems}
        \item {Co-developed a full stack solution for CrimeStoppers Tasmania's online crime reporting website with future support for multi-tenancy. Achieved media press recognition and awards. A site accessible to the public to report crimes anonymously and upload media. Fully mobile responsive and near real-time management portal to process reports submitted by the public and stream media backed by an identity server. Features such as searching, filtering, pagination, audit logs, permissions, downloading, report statistics implemented in the portal.}
		\item {Maintained and developed a legacy product by an ex-Motorola employee. The project sends email notifications to customers in the case of an outage to their service. Reworked the app months later into a modern web application with a fine grained permission system backed by Google account authentication. Increased productivity and decreased the need of supporting the application vastly.}
        \item {Performed over the air (OTA) updates to RACV owned tablets adding various software updates and patches for security/requirements from client liaising.}
		\item {Modified an existing app written in C\# \& WPF to support Push-to-talking radios over a Bluetooth connection. Automated the way of doing a manual tedious task, increasing the efficiency of our office vastly.}
        \item {Developed a web application to efficiently configure hundreds of routers to be installed in Ambulance Victoria vehicles. The app performed various file I/O reading and writing in an easy to use user interface.}
        \item {Performed various amounts of testing with clients in person and over calls. Liaising with mission-critical tenants (Ambulances, Police officers, Firefighters} to develop, test and pass software updates to be pushed live across the state.
      \end{cvitems}
    }
  \cventry
    {Python, GIT, Markdown, AI}
    {Artifical Intelligence: Pacman AI CTF Contest}
    {RMIT University}
    {Oct. 2020}
    {
      \begin{cvitems}
        \item {Developed a Pacman AI using numerous techniques such as A* Search, Expectimax \& Reinforcement Learning/Q-Learning with function approximation in a group of 3 team members (inclusive).}
        \item {Finished at 3rd place out of 74 teams total for best AI (groups of 3-4 in each team).}
      \end{cvitems}
    }
\end{cventries}
